Essays in Computational Management Science

### 2018-08-02 Chapters/Introduction.tex
papers TODO
sdm ready?

Bitcoin is the first and most famous cryptocurrency, used worldwide, with a highly volatile market cap, as of this writing, of \$ 192 bi. Even so, it faces serious scalability challenges; such as serious quality of service and network congestion when the number of transactions per second is high, and an increase in the transaction fees and uncertain delays in transactions' confirmations.

@@

\emph{Iota} is a second cryptocurrency that, instead of using a blockchain, proposes the use of a ``tangle' architecture': a different way to register the currency ledger across thousands of computers. Although it has not been confirmed in practice yet, its architecture seems to be significantly more scalable than Bitcoin's blockchain. As we will see, the problem here is exactly the opposite of Bitcoin's. Iota needs a minimum of transactions per seconds in order to work properly.

Our analysis suggests an architecture for a distributed currency which is inspired in both Bitcoin's blockchain and Iota's tangle in order to solve the scalability problems. While Bitcoin's network saturates when it hits a certain number of transactions per second, Iota's does not work properly with less than a certain number of transactions per second. Our proposed architecture seems to work in both scenarios: low and high number of transactions per second.

@@

A second topic that may have an outsized influence on business and that we will be taking a closer look is a model of artificial intelligence --- and of human decision making.

@@

Beyond a formalization of this process of memory recall, Sparse Distributed Memory will offer us a plausible, both psychologically and neuroscientifically, path towards artificial intelligence.  We'll need to take a turn here.

@@

Technology has been one of the underlying engines behind economic growth. It has been changing the whole society -- people, companies, and governments. Cities and houses had to be rethought when cars became popular. Trains allowed distant places to exchange high volume of goods. Airplanes and boats opened countries to overseas business. And, finally, the internet has had a profound impact in nearly everyone's life, as it changed everything -- from the way we communicate, behave, do business, do shopping, share ideas, and so forth.

@@

Artificial intelligence has been disrupting many businesses. Uber is able to handle hundreds of thousands of requests. Amazon optimizes the location of each product based on demand. Netflix increases the quality of their services offering movies specific to the taste of each customer. Spotify learns which kind of music users like the most and suggests playlists. Banks prevent fraud classifying which patterns seem to be erratic towards their customers' previous behavior.

It is gradually becoming impossible to imagine a world without artificial intelligence.

Behind artificial intelligence systems, there is pattern recognition: The capacity to match information from new data with information which has already been seen and is stored in memory. It may be used in classification, face recognition, character recognition, and so forth.  Even if AI cannot yet solve numerous hard problems --- such as the Turing Test, Bongard Problems or simply understanding when `Lawyers are sharks' \citep{french1990subcognition, french2000turing, linhares2000glimpse, french2001co} ---, it is clear that the technology must be taken seriously.

@@

>>>>

Bitcoin is the first and most famous cryptocurrency, used worldwide, with a highly volatile market cap, as of this writing, of \$ 192 B. Even so, it faces serious scalability challenges; such as serious quality of service and network congestion when the number of transactions per second is high, and an increase in the transaction fees and uncertain delays in transactions' confirmations.

@@

\emph{Iota} is a second cryptocurrency that, instead of using a blockchain, proposes the use of a ``tangle architecture'': a different way to register the currency ledger across thousands of computers. Although it has not been confirmed in practice yet, its architecture seems to be significantly more scalable than Bitcoin's blockchain. As we will see, the problem here is exactly the opposite of Bitcoin's. Iota needs a minimum number of transactions per second in order to work properly.

Our analysis suggests an architecture for a distributed currency which is inspired by both Bitcoin's blockchain and Iota's tangle in order to solve the scalability problems. While Bitcoin's network saturates when it hits a certain number of transactions per second, Iota's does not work properly with less than a certain number of transactions per second. Our proposed architecture seems to work in both scenarios: low and high number of transactions per second.

@@

A second topic that may have an outsized influence on business and that we will be taking a closer look at is a model of artificial intelligence --- and of human decision making.

@@

Beyond a formalization of this process of memory recall, Sparse Distributed Memory will offer us a plausible, both psychologically and neuroscientifically, path towards artificial intelligence.

@@

% Jamil: Se quiser citar algo, tem os papers do Solow (1956, 1957) ou o Advanced Macroeconomics do Romer (2016).
Technology has been one of the underlying engines behind economic growth. It has been changing the whole society -- people, companies, and governments. Cities and houses had to be rethought when cars became popular. Trains allowed distant places to exchange high volume of goods. Airplanes and boats opened countries to overseas business. And, finally, the internet has had a profound impact in nearly everyone's life, as it changed everything -- from the way we communicate, behave, do business, do shopping, share ideas, and so forth.

@@

Artificial intelligence has been disrupting many businesses. Uber is able to handle hundreds of thousands of requests. Amazon optimizes the location of each product based on demand. Netflix increases the quality of their services offering movies specific to the taste of each customer. Spotify learns which kind of music users like the most and suggests playlists. Banks prevent fraud by classifying which patterns seem to be erratic towards their customers' previous behavior.

% Jamil: Não gosto de parágrafos soltos de uma frase em textos acadêmicos. Questão de estilo, mas comentando por comentar.
It is gradually becoming impossible to imagine a world without artificial intelligence.

Behind artificial intelligence systems, there is pattern recognition: the capacity to match information from new data with information which has already been seen and is stored in memory. It may be used in classification, face recognition, character recognition, and so forth.  Even if AI cannot yet solve numerous hard problems --- such as the Turing Test, Bongard Problems or simply understanding when `Lawyers are sharks' \citep{french1990subcognition, french2000turing, linhares2000glimpse, french2001co} --- it is clear that the technology must be taken seriously.

@@

% Jamil: Convém expandir um pouco mais isso aqui. Qualidade muito discrepante com as outras subseções do capítulo.
